%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


    %---------------------------------------------------------
   	\cventry
	{Solutions Architect} % Job title
	{Jive Investments} % Organization
	{SP, Brasil} % Location
	{Ago. 2021 - mar. 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Execution of agile methodologies and OKRs in culture.}
			\item {Growth and maturation of the technology team; from 10 to 50 people.}
			\item {Legacy code migration: monolithic -> microservices \& on-premise -> cloud.}
			\item {Leadership of development teams to adopt new technologies.}			
			\item {Communication and stakeholder guidance for M\&As.}			
			\item {Implementation of Data-Lake-House and improvement of data ingestion processes.}
			\item {ServiceNOW migration plan and contract/price negotiation.}
			\item {Research and development of new tools for the company's strategic innovation \& portfolio/contract management. }
			\item {Adequacy of regional laws for tax reduction.}			
			\item {Implementation of TOGAF architecture standards for compliance with the COBIT framework.}
			\item {Legacy/future environment design using C4 and archimate. Domain Driven Design.}
			\item {Creation of a Webscrapping Platform.}					
		\end{cvitems}
	}
 
     \cventry
    {FullStack Senior Developer} % Job title
    {Stefanini} % Organization
    {SP, Brasil} % Location
    {Fev. 2020 - Jan. 2021} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {SAFE module customization on the ServiceNOW platform.}
    		\item {Development of advanced reports using D3.js.}    		
    	\end{cvitems}
    }
    \cventry
    {FullStack Senior Developer} % Job title
    {AOOP Cloud Solutions} % Organization
    {SP, Brasil} % Location
    {Fev. 2019 - Set. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Correction of problems and implementation of best practices in multiple ServiceNOW environments.}
        \item {Development of a cryptographic API in Python, which is consumed by a portal in ServiceNOW.}
        \item {Dynatrace injection into a cross-platform react-native mobile application.}
      \end{cvitems}
    }   
	\cventry
	{FullStack Mid-level Developer} % Job title
	{Organize Cloud Labs.} % Organization
	{SP, Brasil} % Location
	{Mai. 20018 - Dez. 2018} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Development/Customization with the ServiceNOW platform (Cloud process manager based on ITIL).}
			\item {Expertise in customer training.}
		\end{cvitems}
	}

\end{cventries}

