%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}
\vspace{5mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Programming languages} % Category
    {Javascript, Python, RUST, R , Elixir, C++ (Arduino), GoLang, Solidity, Shell Script e Clojure.} % Skills
    %---------------------------------------------------------
  \cvskill
    {Cloud} % Category
    { ServiceNon, AWS, Azure, Google, Heroku. With Terraform and others DevOPS tools.} % Skills

%---------------------------------------------------------
  \cvskill
    {Frameworks} % Category
    {Express, AngularJS, React ( Redux, redux-thunk ), React-Native, Vue.js , Jasmine , Mocha ,  etc ...} % Skills

%---------------------------------------------------------
\cvskill
    {DevOps} % Category
    {Git/GitLab, Selenium, Jenkins, Docker/Kubernets, AWS tools, Prometheus, Dynatrace , Vagrant, etc ...} % Skills

%---------------------------------------------------------
 \cvskill
    {Statistics \& BigData} % Category
    { R (functional language), Jupyter Notebook, python spider, Hadoop with Spark (HortonWorks/AWS).
    } % Skills

%---------------------------------------------------------
 \cvskill
    {Blockchain} % Category
    { Geth, Tuffle-ENV, Smarth contracts with Solidity.} % Skills

%---------------------------------------------------------
 \cvskill
    {Data Bases} % Category
    {Relacional : MySQL/MariaDB , NoSQL : MongoDB/AWSDynamoDB, Graph: Neo4j/AWSNeptune.} % Skills

%---------------------------------------------------------
 \cvskill
    {Design} % Category
    {Figma,Procreate, Photoshop, Illustrator, After Effects e GIMP.} % Skills
    
%---------------------------------------------------------
 \cvskill
    {Project management} % Category
    {Agile/SAFe/Extreme-Programming/Clean. Scrum and PMBOK.} % Skills
%---------------------------------------------------------
 \cvskill
    {Hardware and IoT} % Category
    { C++ with arduino, python libraries for raspberry pi, Zetta server and IoT Home Assistant} % Skills
%---------------------------------------------------------
\cvskill
{Cybersecurity} % Category
{ Real hackers make their own tools. See my github ;D} % Skills
%---------------------------------------------------------
\cvskill
{Software Architecture} % Category
{ ADM \& TOGAF, COBIT . Archimate with C4 , MDL and UML . EventStorm, DDD etc... } % Skills
%---------------------------------------------------------
 \cvskill
 {Línguas} % Category
 { English and Portuguese (fluent).} % Skills

%---------------------------------------------------------
\end{cvskills}
